Visual Search and Pre-crastination

### 2023-12-20 RegReport/paper_nomarkup.tex
minor final edits

We collected data from a grand total of 305 participants. 14 of these participants had to be removed due to missing eyetracking data. Out of the 291 remaining, 90 failed to meet our inclusion criteria for the visual search task\footnote{further details available in supplementary materials}. This leaves us with 201 participants with visual search data. 303 participants completed the precrastination task (one participant was excused from this part of the experiment because of a brokem leg, and another for an unspecified reason). 304 participants completed the personality questionnaires (XXX participants had blank or otherwise unusable data).

@@

Each participant’s median reaction time and accuracy was computed for the split-half visual
search task, presented in Figure \ref{fig:exp2_summary}. The results are broadly in-line with those that we have seen in previous uses of this paradigm. More importantly, we see large variation in search strategy (\ref{fig:exp2_strat_summary}(a), replicating previous results.

@@

We met all outcome-neutral conditions and acquired a sample sufficient in size and quality to test the three hypotheses. As with the pilot data, the larger sample demonstated that precrastination behaviour is common, with more than half the participants picking up the close bucket first. We also replicated the wide range of variation between individuals in visual search effiency. We found no evidence for a consistent relationship between visual search effiency and precrastination, however, and no relationship between either measure and conscientiousness. Therefore, no evidence in favor of our registered hypotheses resulted from this experiment.

@@

\subsubsection{Personality and Visual Search Strategy}
The right column of Figure \ref{fig:exp_analysis} shows the relationship between 10 personality measures and visual search strategies, expressed as a correlation between effiency score (proportion of fixations on the heterogeneous side) and score on each scale/subscale.  We find no evidence of any clear relationships between the personality measures and visual search strategy in this sample of 201 participants.

@@

\section{General Discussion}
Although the pilot data suggested participants who pre-crastinate tended to use their peripheral vision to search more efficiently, the registered study with a much larger sampledid not support that conclusion. While this is a null finding, it is nonetheless meaningful because we had a clear prediction based on data and theory and designed a robust experiment to test it, which underwent rigourous peer review. Both the pilot and the final experiment replicated the previously-established patterns in finding (1) a good split of people who consistently pre-crastinated and people who consistently did not and (2) a broad range of individual differences in visual search efficiency. If a stable relationship between these factors exists and is large enough to build any theories around, this experiment would have detected it. The fact that it did not detect it is useful in ruling out explanations for either behaviour (precrastination or visual search inefficiency) that is grounded in a shared personality characteristic like conscientiousness or impulsivity.

>>>>

We collected data from a grand total of 305 participants. 14 of these participants had to be removed due to missing eyetracking data. Out of the 291 remaining, 90 failed to meet our inclusion criteria for the visual search task\footnote{further details available in supplementary materials}. This leaves us with 201 participants with visual search data. 303 participants completed the precrastination task (one participant was excused from this part of the experiment because of a \textcolor{red}{broken} leg, and another for an unspecified reason). 304 participants completed the personality questionnaires (\textcolor{red}{20} participants had blank or otherwise unusable data).

@@

Each participant’s median reaction time and accuracy was computed for the split-half visual
search task, presented in Figure \ref{fig:exp2_summary}. The results are broadly in-line with those that we have seen in previous uses of this paradigm. More importantly, we see large variation in search strategy (\ref{fig:exp2_strat_summary}(a), replicating previous results. \textcolor{red}{The standard deviation of our efficiency score is 0.192.}

@@

We met all outcome-neutral conditions and acquired a sample sufficient in size and quality to test the three hypotheses. As with the pilot data, the larger sample demonstrated that precrastination behaviour is common, with more than half the participants picking up the close bucket first. We also replicated the wide range of variation between individuals in visual search efficiency. We found no evidence for a consistent relationship between visual search efficiency and precrastination, however, and no relationship between either measure and conscientiousness. Therefore, no evidence in favor of our registered hypotheses resulted from this experiment.

@@

\subsubsection{Personality and Visual Search Strategy}
The right column of Figure \ref{fig:exp_analysis} shows the relationship between 10 personality measures and visual search strategies, expressed as a correlation between efficiency score (proportion of fixations on the heterogeneous side) and score on each scale/subscale.  We find no evidence of any clear relationships between the personality measures and visual search strategy in this sample of 201 participants.

@@

\section{General Discussion}
Although the pilot data suggested participants who pre-crastinate tended to use their peripheral vision to search more efficiently, the registered study with a much larger sample did not support that conclusion. While this is a null finding, it is nonetheless meaningful because we had a clear prediction based on data and theory and designed a robust experiment to test it, which underwent rigourous peer review. Both the pilot and the final experiment replicated the previously-established patterns in finding (1) a good split of people who consistently pre-crastinated and people who consistently did not and (2) a broad range of individual differences in visual search efficiency. If a stable relationship between these factors exists and is large enough to build any theories around, this experiment would have detected it. The fact that it did not detect it is useful in ruling out explanations for either behaviour (precrastination or visual search inefficiency) that is grounded in a shared personality characteristic like conscientiousness or impulsivity.

### 2023-12-20 analysis/3_exploratory.Rmd
minor final edits

  r_beads <- cor.test(dat$n_beads, dat[[measure]])

  d_out <- tibble(measure = measure,
                  lower = c(r$conf.int[[1]], d$conf.int[[1]], r_beads$conf.int[[1]]),
                  upper = c(r$conf.int[[2]], d$conf.int[[2]], r_beads$conf.int[[2]]),
                  feature = c("search", "pre-crastination", "beads"))
  return(d_out)
}

@@

dr$col <- as_factor(rep(c(1,1,1,1,2,2,2,2,2,3), each = 3))

>>>>

  #r_beads <- cor.test(dat$n_beads, dat[[measure]])

  d_out <- tibble(measure = measure,
                  lower = c(r$conf.int[[1]], d$conf.int[[1]]),#, r_beads$conf.int[[1]]
                  upper = c(r$conf.int[[2]], d$conf.int[[2]]), #  r_beads$conf.int[[2]]
                  feature = c("search", "pre-crastination")) #, "beads"
  return(d_out)
}

@@

dr$col <- as_factor(rep(c(1,1,1,1,2,2,2,2,2,3), each = 2))
